The paper on \Large \bf Blockchain Frontrunning

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] editted till section 5 (5 On Blockchain Front-running)

The concept of the \emph{front-running} goes back to the decades ago when financial instrument markets first started. Initially the trades required to be physically available in the exchange office to deliver the bids and offers, and traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However with the rapid advances of the technology in the last few decades, trading is not happening in person anymore and a greater number of applications are now vulnerable to front-running. Furthermore, Blockchain technology has introduced transparency and open markets which led to a new threat of front-running and it inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain. However, the goal of this paper is to provide a complete look at the front-running issues and thus the aforementioned will remain out of the scope of this research study. There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases. \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention". }

%For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.
% Why is this important.
% PAPER BEING SOLD HERE
%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a Bancor case study: 1) here is the bancor project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}

@@

\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades. This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets. In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock. In other words, a group of market participants obtain non-public market information which allows them to front-run other users trades by putting their orders a head of those trades and benefit from advance knowledge of pending client orders. The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}. Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.

@@

Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in Satoshi Nakamoto's (pseudonymous) 2008 white paper \cite{nakamoto2008bitcoin}. Many decentralized applications that are nowadays built on top of this technology represent the significance of the blockchain as it completely eliminates the single points of failures within any systems. However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front running} behaviour. Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders. Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front running. Decentralized exchanges are a group of blockchain financial applications where front running can be executed. Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in Section ...). Decentralized namespaces, as blockchain non-financial applications, are another example. Ghazal \cite{moosavighazal} is such system in which upon seeing a transaction from Alice to register \texttt{alice.com}, front runner can go ahead of her and register this domain name. He can later sell \texttt{alice.com} to Alice for a higher price and benefit from the price increase.
Another application that is vulnerable to front running is Initial Coin Offering, ICO, smart contracts. ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum. After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction, dynamic ceilings, \eg ~\cite{kaal2017initial}.  This competition made ICOs a good opportunity for front-running attacks.  In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts. %TODO: this last sentece is a bit weird here!

%___________________________________________________________%
\section{Related Work}
As the traditional front-running was originated to trading financial instruments most of the literature are focused on financial aspects of the markets. %TODO: expand this with something

\subsection{Literature on Traditional Front-running}

As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and regulations to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behavior on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBoE).}
\end{quote}

As defining what exactly is considered illegal front-running required more knowledge of how these new markets behave, \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running. However difference of opinion regarding the unfairness of front running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.

@@

\subsection{Literature on Blockchain Front-running}
%NOTE (ASK JEREMY): decentral or decentralized?
There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. \\

Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach to prevent any decentralized system from front-running. In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.

Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.  They argue that blockchain brings a new options of transparency which affects traders behavior, specially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.

Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. They propose \textit{Submarine Commitments} which is to conceal the bounty claim and the participatory factor. They claim submarine commitments ``are a stronger form of a commit-reveal scheme''.

One of the properties of Blockchain technology was to overcome double-spend, however this does not apply for fast payments and zero-confirmation transactions. \textit{Double-spend attack}, as the name implies, the adversary spends a coin more than one time. To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}. This adversarial behavior is similar to the front-running attack where the attacker would front-run other users by paying a higher transaction fee when broadcasting his transactions to the network, hence a higher priority transaction for miners to include in the block they mine.

@@

\section{Status ICO} 
As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, Status ICO is such application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached its cap within 3 hours, resulted in close to 300,000 Ether of funding. In order to prevent large investments to take place early and limit the amount of Ether deposited in an investment, the team at the Status ICO used a \textit{fair} token distribution method called \textit{dynamic ceiling} as an attempt to increase the time window for smaller investors. They implemented multiple caps --ceiling-- which each had a maximum amount that could be deposited. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to the Status.im wallet ~\cite{statusicoanalysis}.

During the time the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming. Further study showed that some mining pools might have been manipulating the network for their own profit. In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failed due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the aforementioned front-running).

@@

According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started. On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions.

Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behavior of the participants and miners solely using the default clients nor online blockchain explorers. In order to get the required data, Ethereum blockchain data should be converted to a queryable format. For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}. Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}. A copy of this dataset and the findings can be found in \texttt{github.com / ANONYMOUS}.

As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running. \textit{Successful Transactions} are the transactions that led to deposit and generation of Status.im tokens and \textit{Failed Transactions} are the transactions to the token sale smart contract that failed to retrieve any tokens, for varias reasons.  It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

@@

%TODO: describe failed/ successful transactions, what they mean!

By tracing the transactions from these 30 addresses, we found a explicit Interference of the F2Pool in this scenario. As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool. Once the dynamic ceiling algorithm refunded a portion of the sent funds back to these addresses, these funds were again sent back to F2Pool main address.

@@

Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in a certain way to front-run other transactions and take advantage of the monetary profit. The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}. This analysis made us wonder, how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?

@@

\subsubsection{Exchanges.}
Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their orderbooks are stored on a central server they control and shown on their user interface (website). Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs. Similarly 0xProtocol uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating. One main issue with these exchanges is \textit{cancellation grief}. Although the orderbooks are not in the smart contract, in order to prevent denial of service attacks, user needs to send a transaction to cancel her order. In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is cancelled. As mentioned in ~\ref{minersfrontrunning}, miners are in a better control to perform such attack.

@@

\subsubsection{Design Decision \#2: Submarine Commitments\newline}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized. However, they could be design in other ways to suit the need of the DApp. With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.

>>>>

The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started. Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However with the rapid advances of the technology in the last few decades, trading is not done in person anymore and new generation front-running was feasible through high speed networks. Furthermore, Blockchain technology has introduced transparency and open markets which led to a new era of front-running and it inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain. We started by looking at one specific case of front-running on Ethereum blockchain, However, the goal of this paper is to provide a complete look at the front-running issues. %and thus the aforementioned will remain out of the scope of this research study.
There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases. \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention". }

% PAPER BEING SOLD HERE
%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a status,im ico case study: 1) here is the status.im ico project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}

@@

\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades. This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as it was originated back in stock markets. In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would now run in front of that order and put his own transaction in-between (before the trade was executed) and profit from the price increase of the stock. In other words, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders. The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}. Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.

@@

Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}. Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems. However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behavior. Although this data structure is known to be publicly visible to every network participants, information is layered  and some of them are accessed only by insiders. Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running. Decentralized exchanges are a group of blockchain financial applications where front-running can be executed. 
Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}). Decentralized namespaces, as blockchain non-financial applications, are another example. Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name. He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts. ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum. After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.  This competition made ICOs a good opportunity for front-running attacks.  In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts. %TODO: this last sentece is a bit weird here!

%___________________________________________________________%
\section{Related Work}
As the traditional front-running was originated in trading financial instruments most of the literature are focused on financial aspects of the markets.  However, there are also a few policies regarding domain name registration front-running~\cite{sac022en33:online}

\subsection{Literature on Traditional Front-running}
As traditional front-running has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange (\textit{CBoE})~\cite{markham1988front}, and was defined by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and policies to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behavior on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBoE).}
\end{quote}

Defining what exactly was considered illegal front-running required more knowledge of how these new markets behaved. \textit{CBoE} and other exchanges (and brokers) issued educational circulars for their members asserting that front-running violates existing rules, with some examples of what is considered front-running. However difference of opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action by self-regulator organizations~cite{sec1978optionsmarket}.

@@

\subsection{Literature on Blockchain Front-running}
There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. \\

Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach, similar to commit and reveal(~ref{CommitmentScheme}), to prevent front-running in decentral systems. %In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.  They argue that blockchain brings a new options of transparency which affects traders behavior, specially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.

Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} (~\ref{submarineCommits}).

One of the properties of Blockchain technology was to overcome double-spend, however this does not apply for fast payments and zero-confirmation transactions. \textit{Double-spend attack}, as the name implies, the adversary spends a coin more than one time. To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}. This adversarial behavior is similar to the front-running attack where the attacker front-runs his own transaction by paying a higher fee when broadcasting the second transaction.

@@

\section{Status ICO} 
As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds. In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors. They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address ~\cite{statusicoanalysis}.

During the time the ICO was open for participation, there were reports of Ethereum network being unusuable and transactions were not confirming. Further study showed that some mining pools might have been manipulating the network for their own profit. In addition, there were many transactions sent with higher gas price to front-run other transactions, however these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (as an attempt to prevent the known front-running behavior).

@@

According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started. On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.

Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behavior of the participants and miners solely using the default clients nor online blockchain explorers. In order to get the required data, Ethereum blockchain data should be converted to a queryable format. For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}. Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}. A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.

As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract. The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running. It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

@@

By tracing the transactions from these 30 addresses, we found explicit Interference of the F2Pool\footnote{F2Pool Ethereum address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}} in this scenario. As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after.

@@

Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and take advantage of the monetary profit. The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}. This analysis made us wonder how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?

@@

\subsubsection{Exchanges.} \label{sec:frontrunningExchanges}
Exchanges such as EtherDelta\footnote{also known as ForkDelta for the UI \url{https://forkdelta.app/}}, are closest form to decentral exchanges, however their orderbooks are stored on a central server they control and shown on their user interface (website). Other than the fact that they can re-order or censor the orders on their servers, there are other risks of front-running nature in these designs. Similarly 0xProtocol uses \textit{Relayers} which act as the orderbook holders and are not prune to cheating. One main issue with these exchanges is \textit{cancellation grief}. Although the orderbooks are not in the smart contract, in order to prevent denial of service attacks, user needs to send a transaction to cancel her order. In this case, when an adversarial actor sees the cancellation transaction, he sends a fill order transactions with higher gasPrice to get in front of the cancellation order and take the order before it is cancelled. As mentioned in ~\ref{minersfrontrunning}, miners are in a better control to perform such attack.

@@

\subsubsection{Design Decision \#2: Submarine Commitments\newline}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized. However, they could be design in other ways to suit the need of the DApp. With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.
